# Conventions {#sec-conventions}

This book will use the following conventions:

* Code: `list(number = 1, letter = "A")`
* File paths: <path>data/sales.csv</path>
* Menu/interface options: <if>Tools > Global Options... > Pane Layout</if>
* R Packages: <pkg>tidyverse</pkg>
* Glossary items: `r glossary("ordinal")`
* Citations: @usethis
* Internal links: @sec-conventions
* External links: [Mastering Shiny](https://mastering-shiny.org/){target="_blank"}
* Mac-specific: <mac>Cmd-Shift-F10</mac> 
* Windows-specific: <pc>Ctl-Shift-F10</pc>

A list of mac and windows [keyboard shortcuts](https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE).


## Test Yourself

I am going to learn a lot: `r torf(TRUE)`

```{r, echo=FALSE, results='asis'}
opts <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)

cat("* What is a p-value?", longmcq(opts))
```


```{block, webex.hide="Hidden Solutions"}
You found it!
```

## Callout boxes

[See the [quarto reference](https://quarto.org/docs/authoring/callouts.html) for more options.]{.aside}

::: {.callout-note}
Informational asides.
:::

::: {.callout-note collapse="true"}
## Click to expand
Expanded!
:::

::: {.callout-tip}
Tips
:::

::: {.callout-warning}
Notes to warn you about something.
:::

::: {.callout-caution}
Notes about things that could cause serious errors.
:::

::: {.callout-important}
Notes about things that are important.
:::


## Code and Output

```{r}
# code chunks
paste("Code", "Output", 1, sep = " ")
```

```{r, filename = "Filename or header"}
# code chunks with filename
a <- 1
```

```{r, eval = FALSE, verbatim="r, fig.width = 2, fig.height = 2"}
# code chunks with visible headers
hist(rnorm(100000))
```

```{verbatim, lang = "md"}
## Markdown Example

* Inline code: `r nrow(iris)`
* *Italics*
* **Bold**
* [Linked text](https://psyteachr.github.io)
```



