# How to Use this Book {#sec-instructions}

## Setup {#sec-setup}


### Crossrefs {#sec-crossrefs}

Internal links look like this: @sec-settings

```{verbatim, lang = "md"}
## Section Title {#sec-section-title}

Internal links look like this: @sec-section-title
```

See the [quarto documentation](https://quarto.org/docs/books/book-crossrefs.html){target="_blank"} for more information.

### References {#sec-refs}

Zotero export - keep updated


### Snippets {#sec-snippets}

Copy these to snippets....

Markdown:

```
snippet h1
	# ${1:title} {#sec-${2:ref}}
	
snippet h2
	## ${1:title} {#sec-${2:ref}}
	
snippet h3
	### ${1:title} {#sec-${2:ref}}
	
snippet h4
	#### ${1:title} {#sec-${2:ref}}
	
snippet h5
	##### ${1:title} {#sec-${2:ref}}
```


## Layout {#sec-layout}

### Conventions {#sec-conventions}

This book will use the following conventions:

* Code: `list(number = 1, letter = "A")`
* File paths: <path>data/sales.csv</path>
* Menu/interface options: <if>Tools > Global Options... > Pane Layout</if>
* R Packages: <pkg>tidyverse</pkg>
* Glossary items: `r glossary("ordinal")`
* Citations: @usethis
* Internal links: @sec-conventions
* External links: [Mastering Shiny](https://mastering-shiny.org/){target="_blank"}
* Mac-specific: <mac>Cmd-Shift-F10</mac> 
* Windows-specific: <pc>Ctl-Shift-F10</pc>

A list of mac and windows [keyboard shortcuts](https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE).


### Figures {#sec-figures}

Best practice, set a custom ggplot theme:

```{r}
library(ggplot2)

theme_set(theme_bw() + 
            theme(panel.background = element_rect(fill = "red", color = "black", size = 10))
          )
```


```{r}
ggplot(iris, aes(Sepal.Width, Petal.Width)) +
  geom_point()
```

### Tables {#sec-tables}

Shorter tables and PDFs print using <pkg>kableExtra</pkg> and longer tables in HTML format use <pkg>DT</pkg> for interactive paged tables.

```{r tbl-short}
#| tbl-cap: "Shorter table"
head(beaver1)
```

```{r tbl-long}
#| tbl-cap: "Longer table"
DT::datatable(beaver1)
```

### Callout boxes {#sec-callout}

[See the [quarto reference](https://quarto.org/docs/authoring/callouts.html) for more options.]{.aside}

::: {.callout-note}
Informational asides.
:::

::: {.callout-note collapse="true"}
## Click to expand
Expanded!
:::

::: {.callout-tip}
Tips
:::

::: {.callout-warning}
Notes to warn you about something.
:::

::: {.callout-caution}
Notes about things that could cause serious errors.
:::

::: {.callout-important}
Notes about things that are important.
:::


### Code and Output {#sec-code-output}

```{r}
# code chunks
paste("Code", "Output", 1, sep = " ")
```

```{r, filename = "Filename or header"}
# code chunks with filename
a <- 1
```

```{r, eval = FALSE, verbatim="r, fig.width = 2, fig.height = 2"}
# code chunks with visible headers
hist(rnorm(100000))
```

```{verbatim, lang = "md"}
## Markdown Example

* Inline code: `r nrow(iris)`
* *Italics*
* **Bold**
* [Linked text](https://psyteachr.github.io)
```







### Fonts {#sec-fonts}




## Best Practices {#sec-best-practices}

### Glossary {#sec-glossary}

Look up a term from the glossary file with `glossary("alpha")`: `r glossary("alpha")`

Display a different value for the term with `glossary("alpha", "$\\alpha$")`: `r glossary("alpha", "$\\alpha$")`

Use an inline definition instead of the glossary file with `glossary("beta", def = "The second letter of the Greek alphabet")`: `r glossary("beta", def = "The second letter of the Greek alphabet")`

Just show the definition with `glossary("p-value", show_def = TRUE)`: `r glossary("p-value", show_def = TRUE)`

Show the table of terms defined on this page with `glossary_table()`:

```{r, echo = FALSE}
glossary_table()
```



### Webexercises {#sec-webexercises}

<!-- copy from webexercises page -->

I am going to learn a lot: `r torf(TRUE)`

```{r, echo=FALSE, results='asis'}
opts <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)

cat("* What is a p-value?", longmcq(opts))
```


```{block, webex.hide="Hidden Solutions"}
You found it!
```

<!--
add_to_quarto() function

Add button for delayed feedback 
Fence off "Quiz Yourself"
-->
