# Overview {.unnumbered}

Welcome to the quarto textbook template. To get started editing the book, open up the 

## Settings {#sec-settings}

Most of the settings are in the configuration file: <path>_quarto.yml</path>. See the [quarto documentation](https://quarto.org/docs/books/#config-file){target="_blank"} for more information. 

## Tables {#sec-tables}

Shorter tables and PDFs print using <pkg>kableExtra</pkg> and longer tables in HTML format use <pkg>DT</pkg> for interactive paged tables.

```{r tbl-short}
#| tbl-cap: "Shorter table"
head(beaver1)
```

```{r tbl-long}
#| tbl-cap: "Longer table"
DT::datatable(beaver1)
```

## Crossrefs {#sec-crossrefs}

Internal links look like this: @sec-settings

```{verbatim, lang = "md"}
## Section Title {#sec-section-title}

Internal links look like this: @sec-section-title
```

See the [quarto documentation](https://quarto.org/docs/books/book-crossrefs.html){target="_blank"} for more information.

## Glossary

Look up a term from the glossary file with `glossary("alpha")`: `r glossary("alpha")`

Display a different value for the term with `glossary("alpha", "$\\alpha$")`: `r glossary("alpha", "$\\alpha$")`

Use an inline definition instead of the glossary file with `glossary("beta", def = "The second letter of the Greek alphabet")`: `r glossary("beta", def = "The second letter of the Greek alphabet")`

Just show the definition with `glossary("p-value", show_def = TRUE)`: `r glossary("p-value", show_def = TRUE)`

Show the table of terms defined on this page with `glossary_table()`:

```{r, echo = FALSE}
glossary_table()
```
