---
title: "Webexercises"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{webex}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(booktem)
library(webexercises)
```


The goal of `{webexercises}` is to enable instructors to easily create interactive web pages that students can use in self-guided learning. Although `{webexercises}` has fewer features than RStudio's [learnr](https://rstudio.github.io/learnr/) package, it is more lightweight: whereas `{learnr}` tutorials must be either hosted on a shiny server or run locally, `{webexercises}` creates standalone HTML files that require only a JavaScript-enabled browser. It is also extremely simple to use.

## Installation

You can install `{webexercises}` from CRAN using:

```{r install-cran, eval=FALSE}
install.packages("webexercises")
```


## Creating interactive widgets with inline code

The webexercises package provides functions that create HTML widgets using [inline R code](https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf).  These functions are:

| function                | widget         | description                    |
|:------------------------|:---------------|:-------------------------------|
| `fitb()`                | text box       | fill-in-the-blank question     |
| `mcq()`                 | pull-down menu | multiple choice question       |
| `torf()`                | pull-down menu | TRUE or FALSE question         |
| `longmcq()`             | radio buttons  | MCQs with long answers         |
| `total_correct()`       | text           | updating total correct         |

The appearance of the text box and pull-down menu widgets changes when users enter the correct answer. Answers can be either static or dynamic (i.e., specified using R code). Widget styles can be changed using `style_widgets()`.

These functions are optimized to be used with inline r code, but you can also use them in code chunks by setting the chunk option `results = 'asis'` and using `cat()` to display the result of the widget. 

```{r, results = 'asis'}
# echo = FALSE, results = 'asis'
opts <- c("install.package", 
            "install.packages", 
            answer = "library", 
            "libraries")
q1 <- mcq(opts)
cat("What function loads a package that is already on your computer?", q1)
```


### Fill-In-The-Blanks

Create fill-in-the-blank questions using `fitb()`, providing the answer as the first argument.

```{r, eval = FALSE}
fitb(4)
```

- 2 + 2 is `r fitb(4)`

You can also create these questions dynamically, using variables from your R session (e.g., in a hidden code chunk).

```{r echo = TRUE}
x <- sample(2:8, 1)
```

```{r, eval = FALSE}
fitb(x)
```

- The square root of `r x^2` is: `r fitb(x)`



The blanks are case-sensitive; if you don't care about case, use the argument `ignore_case = TRUE`.

```{r, eval = FALSE}
fitb("E", ignore_case = TRUE)
```

- What is the letter after D? `r fitb("E", ignore_case = TRUE)`



If you want to ignore differences in whitespace use, use the argument `ignore_ws = TRUE` (which is the default) and include spaces in your answer anywhere they could be acceptable.

```{r eval = FALSE}
fitb(c("library( tidyverse )", "library( \"tidyverse\" )", "library( 'tidyverse' )"), ignore_ws = TRUE, width = "20")
```

- How do you load the tidyverse package? `r fitb(c("library( tidyverse )", "library( \"tidyverse\" )", "library( 'tidyverse' )"), ignore_ws = TRUE, width = "20")`

You can set more than one possible correct answer by setting the answers as a vector.

```{r, eval = FALSE}
fitb(c("A", "E", "I", "O" , "U"), ignore_case = TRUE)
```

- Type a vowel: `r fitb(c("A", "E", "I", "O" , "U"), ignore_case = TRUE)`

You can use regular expressions to test answers against more complex rules.

```{r, eval = FALSE}
fitb("^[a-zA-Z]{3}$", width = 3, regex = TRUE)
```

- Type any 3 letters: `r fitb("^[a-zA-Z]{3}$", width = 3, regex = TRUE)`

### Multiple Choice

Set up a multiple-choice drop-down menu using `mcq()`.

```{r, eval = FALSE}
mcq(c("tidyr", "dplyr", answer = "readr", "ggplot2"))
```

- What package helps you load CSV files? `r mcq(c("tidyr", "dplyr", answer = "readr", "ggplot2"))`
- "Never gonna give you up, never gonna: `r mcq(c("let you go", "turn you down", "run away", answer = "let you down"))`"
- "I `r mcq(c(answer = "bless the rains", "guess it rains", "sense the rain"))` down in Africa" -Toto

### True or False

Make quick true/false questions with `torf()`.

```{r, eval = FALSE}
torf(TRUE)
torf(FALSE)
```

- True or False? You can permute values in a vector using `sample()`. `r torf(TRUE)`

### Longer MCQs

When your answers are very long, sometimes a drop-down select box gets formatted oddly. You can use `longmcq()` to deal with this. Since the answers are long, it's probably best to set up the options inside an R chunk with `echo=FALSE`. 

```{r, echo = TRUE}
opts_p <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)
```

```{r, eval=FALSE}
longmcq(opts_p)
```

**What is a p-value?**

`r longmcq(opts_p)`

**What is true about a 95% confidence interval of the mean?**

```{r, echo = FALSE}
# use sample() to randomise the order
opts_ci <- sample(c(
  answer = "if you repeated the process many times, 95% of intervals calculated in this way contain the true mean",
  "there is a 95% probability that the true mean lies within this range",
  "95% of the data fall within this range"
))
```

`r longmcq(opts_ci)`

### Hidden solutions and hints

You can fence off a solution area that will be hidden behind a button using `hide()` before the solution and `unhide()` after, each as inline R code.  Pass the text you want to appear on the button to the `hide()` function.

```{r eval = FALSE}
hide("Click here to see the solution")
unhide()
```

If the solution is an RMarkdown code chunk, instead of using `hide()` and `unhide()`, you can set the `webex.hide` chunk option to TRUE, or set it to the string you wish to display on the button.

How do you load tidyverse?

`r hide("Click here to see the solution")`

```{r eval = FALSE}
library(tidyverse)
```

`r unhide()`

<!--
add_to_quarto() function
-->

## Checked sections

::: {.webex-check .webex-box}

I am going to learn a lot: `r torf(TRUE)`

```{r, echo=FALSE, results='asis'}
opts <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)

cat("* What is a p-value?", longmcq(opts))
```

:::

